Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-19 ms.rmd
Updated MS. Knitted

#devtools::install_github(repo = "ErikKusch/KrigR")
## Function to produce colour palette
# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can greate a custom colour palelte function using colorRampPallette
colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
#test colfunc(10) will generate the exact Hex codes for 10 different colours can 10 to 100 and you get 100 colour hex codes. Very useful webpage: https://pjbartlein.github.io/REarthSysSci/rasterVis01.html

@@

  ## Check support for two models
  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het). # Clearly better supported.
      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het

@@

```{r, fig2, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS"))
ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS"))
ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0)
ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
fig2

>>>>

#devtools::install_github(repo = "ErikKusch/KrigR")
## Function to produce colour palette
# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can create a custom colour palette function using colorRampPallette
colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
#test colfunc(10) will generate the exact Hex codes for 10 different colours can 10 to 100 and you get 100 colour hex codes. Very useful webpage: https://pjbartlein.github.io/REarthSysSci/rasterVis01.html

@@

  ## Check support for two models
  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het

@@

```{r, fig2, fig.align='center', eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")
#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
fig2
ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")
```
